Reasoning about a Capability Machine with Local Capabilities\\ Provably Safe Stack and Return Pointer Management (without OS Support)\\ Technical Appendix Including Proofs and Details

### 2017-03-23 fully-abstract-comp/technical-report.tex
notes

Source language:
\begin{itemize}
\item No jumps to enter (call reserved for this)
\item Variable length instructions that match the length of the compiled instructions
  \begin{itemize}
  \item Opaque capabilities do not hide the length of a program (especially an issue if we ever hope to have error recovery).
  \item This is needed for correctness. See subsection~\ref{subsec:capability-opacity} for an example it helps prevent.
  \end{itemize}
\end{itemize}

@@

\clearpage
\section{Back translation}
We want to do the back translation by interpreting the programs.
\end{document}

>>>>

Source language:
\begin{itemize}
\item Variable length instructions that match the length of the compiled instructions
  \begin{itemize}
  \item Opaque capabilities do not hide the length of a program (especially an issue if we ever hope to have error recovery).
  \item This is needed for correctness. See subsection~\ref{subsec:capability-opacity} for an example it helps prevent.
  \end{itemize}
\item Programs have undefined behavior when passing ret/stk pointers.
\end{itemize}

@@

\clearpage
\section{Back translation}
The back translation is an embedding of source language into .

\section{Notes}
\subsection{Leuven stay conclusions}
\begin{enumerate}
\item Enter capabilities replaces by sealed code/data pairs \label{item:first-point}
  \begin{itemize}
  \item To allow us to forbid dynamic code generation
  \end{itemize}
\item Conditional full-abstraction
  \begin{itemize}
  \item No undefined behaviour by \emph{trusted code} in any context implies full-abstraction. (Blame idea: undefined as undef of current pc, so current pc can be checked for whether it was the trusted code).
  \item Avoids dynamic checks to protect trusted code against itself.
  \item Possible due to point \ref{item:first-point}.
  \end{itemize}
\item replace push/pull/call/ret/sload by symbolic return pointer (pair) and stack pointer.
  \begin{itemize}
  \item Allows backtranslation to be embedding into source language.
    \begin{itemize}
    \item Interpreter for backtranslation is not able to accurately replicate code length.
    \end{itemize}
  \end{itemize}
\item Worlds similar to CSF paper, but invariants on seals as well.
  \begin{itemize}
  \item Invariants says what can be sealed with a certain seals.
  \end{itemize}
\item Linker: resolves symbols
  \begin{itemize}
  \item Export refs (Question: do we allow other things than sealed code/data pairs to be exported?)
  \item Import refs
  \item Fresh seal requirement
  \end{itemize}
\item Components are memory segments and symbols.
\item Variable instruction length in the source to avoid leaking information through code size that cannot be matched after compilation (breaks compiler correctness, se example in subsection~\ref{subsec:capability-opacity}).
  \begin{itemize}
  \item Notice x86 allows instructions of up to infinite length, so this is not weird.
  \end{itemize}
\item Have opaque capabilities.
  \begin{itemize}
  \item Without opaque capabilities, stack consumption could be inferred through stack pointer index etc.
  \end{itemize}
\item Considered PORs for transition systems to: (a->b => a=a and b=b)
  \begin{itemize}
  \item Define one region that governs the stack
  \item Make the regions more general
  \item For now, we have not done this: instead we stick with the transition systems we have and have to regions governing the stack reflecting the CSF work.
  \end{itemize}
\end{enumerate}
\end{document}
